---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# BREADR

<!-- badges: start -->
[![R-CMD-check](https://github.com/jonotuke/BREADR/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/jonotuke/BREADR/actions/workflows/R-CMD-check.yaml)
<!-- badges: end -->

The goal of BREADR is to provide an easy-to-use method for estimating degrees of relatedness (up to the second degree) for extremely low-coverage data. BREADR also allows users to quantify and visualise the level of confidence in the estimated degrees of relatedness. 

The method requires Eigenstrat files (an ind, geno and snp file) to begin, allowing the user to account for DNA deamination when genotyping their data. 

## Installation

To install, you can use the usual

```{r, eval=FALSE}
install.packages("BREADR")
```

You can install the development version of BREADR from [GitHub](https://github.com/) with:

```{r, eval=FALSE}
# install.packages("remotes")
remotes::install_github("jonotuke/BREADR")
```

## Contributing to BREADR

Please note that `BREADR` is work in progress! If you are interested in the project and want to know more please feel free to contact Jono Tuke (<simon.tuke@adelaide.edu.au>). If you find a bug or would like to see new or improved features, please open an issue on the [GitHub](https://github.com/jonotuke/BREADR) repository.